Construction of Chebyshev nets with singularities

### 2017-07-07 Article.tex
Correction Theorem 2

Moreover, remark that, since $\varphi$ is a Chebyshev net, it satisfies the following property:
\begin{subequations}\label{eq:courb-geod}
\begin{align}\label{eq:courb-geoda}
\kop_u(u,v) &= -\partial_u\omega(u,v), \\\label{eq:courb-geodb}
\kop_v(u,v) &= \partial_v\omega(u,v),
\end{align}
\end{subequations}
for all $(u,v)\in D$, where $\kop_u:D\to\R$ and $\kop_v:D\to\R$ are respectively the geodesic curvatures of the $u$-coordinate curves and of the $v$-coordinate curves of $\varphi$. We obtain by combining \eqref{eq:cond-bord-c3} and \eqref{eq:courb-geod} that the angle distribution $\omega$ satisfies the boundary conditions
\begin{subequations}\label{eq:cond-bord-angle}
\begin{align}
\omega(u, 0) &= \angle(\gamma_u'(0), \gamma_v'(0)) - \int_0^u\ko_u(s)\ds,\quad\forall u\in[0,L_u],\\
\omega(0,v) &= \angle(\gamma_u'(0), \gamma_v'(0)) + \int_0^v\ko_v(s)\ds,\quad\forall v\in[0,L_v].
\end{align}
\end{subequations}
We first show that we can associate to any angle distribution
$\omega:D\to(0,\pi)$ satisfying \eqref{eq:cond-bord-angle} a unique
mapping $\varphi:=\I(\gamma,\omega):D\to\surf$ satisfying
\eqref{eq:cheb-def-c3b}, \eqref{eq:cond-bord-c3}, and
\eqref{eq:courb-geodb}. We then show that this mapping also satisfies
\eqref{eq:cheb-def-c3a} and \eqref{eq:courb-geoda} whenever $\omega$
satisfies the integrability condition \eqref{eq:cond-integr}. This
section aims at proving the following result:
\begin{theorem}[Existence and uniqueness of Chebyshev nets]\label{thm2full}
Let $\surf$ be a smooth, open, complete, and simply connected
surface. Let $\gamma_u:\R^+\to\surf$ and $\gamma_v:\R^+\to\surf$ be
two smooth curves with respective geodesic curvatures $\ko_u:\R^+\to\R$ and
$\ko_v:\R^+\to\R$, and such that $\gamma_u(0) = \gamma_v(0)$. Suppose
that $\psi=\pi-\angle(\gamma_u'(0),\gamma_v'(0))\in(0,\pi)$ and that
the sector $\Omega$ delimited by $\gamma_u$ and $\gamma_v$
verifies \[\int_{\gamma_u}{\ko_u^+} + \int_{\gamma_v}{\ko_v^-} +
\int_{\Omega}{K^+}<\pi-\psi \text{ and } \int_{\gamma_u}{\ko_u^-} +
\int_{\gamma_v}{\ko_v^+} + \int_{\Omega}{K^-}<\psi.\] Let
$L_u,L_v\in\R_\ast^+\cup\{+\infty\}$ and $D=[0,L_u]\Times[0,L_v]$. Then, there exists
a unique angle distribution $\omega:D\to(0,\pi)$ verifying the
boundary conditions \eqref{eq:cond-bord-angle} and satisfying the
Hazzidakis formula \eqref{eq:hazz-form}, with
$\varphi:=\I(\gamma,\omega): D\to\surf$ the unique mapping satisfying
\eqref{eq:cheb-def-c3b}, \eqref{eq:cond-bord-c3} and
\eqref{eq:courb-geodb}. The mapping $\varphi$ is a smooth Chebyshev net on
$\Omega$ with angles $0<\omega<\pi$.
\end{theorem}

>>>>

Moreover, remark that, since $\varphi$ is a Chebyshev net, it satisfies the following property:
\begin{subequations}\label{eq:courb-geod}
\begin{align}\label{eq:courb-geoda}
\kop_u(u,v) &= -\partial_u\omega(u,v), \\\label{eq:courb-geodb}
\kop_v(u,v) &= \partial_v\omega(u,v),
\end{align}
\end{subequations}
for all $(u,v)\in D$, where $\kop_u:D\to\R$ and $\kop_v:D\to\R$ are respectively the geodesic curvatures of the $u$-coordinate curves and of the $v$-coordinate curves of $\varphi$. We obtain by combining \eqref{eq:cond-bord-c3} and \eqref{eq:courb-geod} that the angle distribution $\omega$ satisfies the boundary conditions
\begin{subequations}\label{eq:cond-bord-angle}
\begin{align}
\omega(u, 0) &= \angle(\gamma_u'(0), \gamma_v'(0)) - \int_0^u\ko_u(s)\ds,\quad\forall u\in[0,L_u],\\
\omega(0,v) &= \angle(\gamma_u'(0), \gamma_v'(0)) + \int_0^v\ko_v(s)\ds,\quad\forall v\in[0,L_v].
\end{align}
\end{subequations}
We first show that we can associate to any angle distribution
$\omega:D\to(0,\pi)$ satisfying \eqref{eq:cond-bord-angle} a unique
mapping $\varphi:=\I(\gamma,\omega):D\to\surf$ satisfying
\eqref{eq:cheb-def-c3b}, \eqref{eq:cond-bord-c3}, and
\eqref{eq:courb-geodb}. We then show that this mapping also satisfies
\eqref{eq:cheb-def-c3a} and \eqref{eq:courb-geoda} whenever $\omega$
satisfies the integrability condition \eqref{eq:cond-integr}. This
section aims at proving the following result:
\begin{theorem}[Existence and uniqueness of Chebyshev nets]\label{thm2full}
Let $\surf$ be a smooth immersion of the plane $\R^2$ in $\R^3$. Let
$\gamma_u:\R^+\to\surf$ and $\gamma_v:\R^+\to\surf$ be two smooth
curves with respective geodesic curvatures $\ko_u:\R^+\to\R$ and
$\ko_v:\R^+\to\R$, and such that $\gamma_u(0) = \gamma_v(0)$. Suppose
that $\psi=\pi-\angle(\gamma_u'(0),\gamma_v'(0))\in(0,\pi)$ and that
the sector $\Omega$ delimited by $\gamma_u$ and $\gamma_v$
verifies \[\int_{\gamma_u}{\ko_u^+} + \int_{\gamma_v}{\ko_v^-} +
\int_{\Omega}{K^+}<\pi-\psi \text{ and } \int_{\gamma_u}{\ko_u^-} +
\int_{\gamma_v}{\ko_v^+} + \int_{\Omega}{K^-}<\psi.\] Let
$L_u,L_v\in\R_\ast^+\cup\{+\infty\}$ and
$D=[0,L_u]\Times[0,L_v]$. Then, there exists a unique angle
distribution $\omega:D\to(0,\pi)$ verifying the boundary conditions
\eqref{eq:cond-bord-angle} and satisfying the Hazzidakis formula
\eqref{eq:hazz-form}, with $\varphi:=\I(\gamma,\omega): D\to\surf$ the
unique mapping satisfying \eqref{eq:cheb-def-c3b},
\eqref{eq:cond-bord-c3} and \eqref{eq:courb-geodb}. The mapping
$\varphi$ is a smooth Chebyshev net on $\Omega$ with angles
$0<\omega<\pi$.
\end{theorem}
